% \special{dvipdfmx:config z 0}
\documentclass[UTF8,a4paper,AutoFakeBold,AutoFakeSlant]{article}
\usepackage[a4paper,left=2.8cm,right=2.6cm,top=3.7cm,bottom=3.5cm]{geometry}
\usepackage{ctex}
% \usepackage{xeCJK}
\usepackage{graphicx}
\usepackage{pythonhighlight}
\usepackage[mathscr]{eucal}
\usepackage{mathrsfs}
\usepackage{booktabs}
\usepackage{capt-of} 
\usepackage{hyperref} 
\usepackage{abstract}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{color}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{enumerate}
\usepackage{amsfonts} 
\usepackage{CJK,CJKnumb}
\usepackage{float}
% \usepackage{gbt7714}
\usepackage{framed}
\usepackage{multirow}
\usepackage{animate}
\usepackage[framemethod=tikz]{mdframed}

\newcommand{\tnewroman}{\fontspec{Times New Roman}}
\newcommand{\song}{\CJKfamily{song}}    % 宋体   (Windows自带simsun.ttf)
\newcommand{\fs}{\CJKfamily{fs}}        % 仿宋体 (Windows自带simfs.ttf)
\newcommand{\kai}{\CJKfamily{kai}}      % 楷体   (Windows自带simkai.ttf)
\newcommand{\hei}{\CJKfamily{hei}}      % 黑体   (Windows自带simhei.ttf)
\newcommand{\li}{\CJKfamily{li}}        % 隶书   (Windows自带simli.ttf) 
\newcommand{\ssong}{\CJKfamily{STSong}}
% \newfontfamily{\heiti}{SimHei}

\xeCJKsetup{SlantFactor = 0.3}
% \xeCJKsetup{SlantFactor = -0.7}
\setCJKmainfont[BoldFont=SimHei, SlantedFont=KaiTi]{SimSun}



\usepackage{xcolor}  	%高亮使用的颜色
\definecolor{commentcolor}{RGB}{85,139,78}
\definecolor{stringcolor}{RGB}{206,145,108}
\definecolor{keywordcolor}{RGB}{34,34,250}
\definecolor{backcolor}{RGB}{220,220,220}

\usepackage{accsupp}	
\newcommand{\emptyaccsupp}[1]{\BeginAccSupp{ActualText={}}#1\EndAccSupp{}}






\title{\textbf{\textsf{{\textsf{Trial Exam I}}}}} 
\author{\tnewroman Yuxiao Ma}
\date{}

% 去掉红框
\hypersetup{
colorlinks=true,
linkcolor=black
}

\renewcommand{\refname}{References}

\begin{document}




\maketitle


\section{Question 1}

\begin{quote}
    Globalisation of knowledge production and regional
innovation policy: Supporting specialized hubs in the
Bangalore software industry
\end{quote}

\subsection{}

Structural components:
\begin{itemize}
    \item Innovation agents: companies in a region’s main industrial clusters,
    including their customers and suppliers. In this sense,
    industrial clusters represent the production component of
    the regional innovation system. In the RIS approach, industrial clusters are defined as the geographic concentration
    of firms in the same or related industries
    \item Stakeholders:  backing up the
    innovative performance of the first type, include research
    and higher education institutes (universities, technical colleges, and R\&D institutes), technology transfer agencies,
    vocational training organizations, business associations,
    finance institutions, etc.  The
    knowledge creating and diffusing organizations provide the
    resources and services (knowledge, capital, etc.) to support
    innovation among the local firms
\end{itemize}


\subsection{}

Crucial processes: 
\begin{itemize}
    \item Interactive learning: crucial for innovation as it is considered to be dependent on
    social capital and  benefits from physical proximity thus enabling innovation will most probably take place when both human capital and social
    capital are in place.
    \item Absorb capacity: the ability of a firm to recognize the value of new, external information, assimilate it, and apply it to commercial ends.
    \item Collaboration with knowledge providers: interaction with universities and research centers.
\end{itemize}


\subsection{}

Components and processes based on shared values:
\begin{itemize}
    \item Interactive learning: this is the centre of innovation and it can benefit the collaboration and trust among the firms as well a knowledge provider and users.
    \item Building absorb capacity:  utilize external knowledge through skilled human capital.
    \item Social capital development \& physical proximity: the trust of social network facilate the interaction and inovation while geographic closeness supports shared norm and may have aggomeration effect.
    \item Policy support: the government support and policy can help to build the infrastructure and stimulate the collaboration among SMEs and research institutions.
\end{itemize}


\subsection{}

Drivers include Interactive learning, absorb capacity, social capital, proximity.

Bottlenecks include the weak local linking and some firms' lack of absorptive capacity.


\subsection{}

Solutions include:
\begin{itemize}
    \item Enhance collaboration: Foster strong networks among SMEs, TNCs, and knowledge institutions to build trust and shared goals.
    \item Strengthen Absorptive Capacity: Provide training and resources to improve firms' ability to absorb and utilize external knowledge.
    \item Government Incentives: Use public procurement to create local markets and support innovative projects.
    \item Promote Proximity Benefits: Encourage co-location of firms and research institutions to enhance collaboration and knowledge sharing.
    \item Support Interactive Learning: Facilitate programs and initiatives that promote interactive learning and continuous innovation.
\end{itemize}



\section{Question 2}

\subsection{}

\begin{itemize}
    \item Major concepts:
\end{itemize}
Blockchain, Peer-to-Peer trading of energy, smart contract, ‘trilemma’: scalability, security, and decentralisation.

\begin{itemize}
    \item Research question:
\end{itemize}

How can blockchain technology address the trilemma of scalability, security, and decentralization in P2P energy trading
and the proposal of a scalable, robust, and secure model to support fast and frequent energy trading.

\begin{itemize}
    \item Resulution:
\end{itemize}

The paper proposes a second-layer solution model to address scalability issues, which processes transactions off-chain and records them on a side-chain to maintain the blockchain's robustness and security.
And proposed solution is empirically tested using data from the RENeW Nexus project, demonstrating its viability in enhancing scalability while maintaining security and decentralization.


\subsection{}

Blockchain-enabled P2P trading allows prosumers to sell surplus electricity directly to consumers without intermediaries, leading to higher earnings compared to feed-in tariffs.
Consumers benefit from potentially lower energy costs and the ability to choose their energy source.
And the decentralized nature of blockchain ensures transparency and security,
so that it reduces the risk with the centralized energy system with intermediaries.


\subsection{}

Agents conducting inclusive research and innovation in STEM actively work to incorporate diverse perspectives and address the needs of underrepresented groups. They prioritize accessibility, equity, and participation in STEM fields, striving to create environments that foster diversity. These agents engage communities, promote interdisciplinary collaboration, and develop policies and practices that ensure all voices are heard and valued in the research and innovation processes.


\subsection{}

Energy-poor people are more likely to become consumers rather than prosumers due to limited resources for investing in energy production infrastructure like solar panels. This disparity could limit the inclusivity of blockchain-enabled P2P energy trading. Without targeted support and policies to assist energy-poor individuals in becoming prosumers, the benefits of this system may be skewed towards those already capable of producing energy, potentially exacerbating existing inequalities. Thus, inclusive measures are crucial for ensuring equitable access and participation in P2P energy markets.


% \bibliographystyle{gbt7714-numerical}
% % \bibliographystyle{7714-author-year}
% \bibliographystyle{ieeetr}
% \bibliography{bibl}


\end{document}
% \bibliography{bibl}


\end{document}in high-tech clusters in the context of 
an emerging economy.

If the policy objective is to increase collaborations and 
knowledge diffusion throughout a cluster, social activities to promote personal connections 
between the owners, managers and researchers in a cluster can be considered as a way of 
complementing traditional grants to enable new formal collaboration.


\subsection{}

The innovation system focus on the network of  institutions, innovative agents 
and the relationships between them. It emphasizes knowledge flows, institutional frameworks, and interactions among various actors. The aim is to improve overall innovation capacity and efficiency by optimizing interactions within the system.

The clustering approach focuses on geographically clustered companies, suppliers, and related institutions, emphasizing the collaboration and knowledge spillovers that come with geographic proximity. The clustering approach emphasizes specialization and competitive advantage among companies within a cluster, aiming to improve innovation ability and competitiveness in a specific region through close connections and synergies between firms.


\subsection{}

Personal proximity promotes collaboration between DBFS by building trust and reducing transaction costs. Previous personal relationships have been shown to significantly increase the likelihood of forming business relationships.

Social proximity Enhances trust and mutual understanding among DBFS through shared norms, values and professional networks. These social ties are consolidated through professional networks such as industry associations and conferences, facilitating knowledge exchange and cooperation.

Geographical proximity Further enhances cooperation between DBFS by promoting frequent face-to-face interaction and effective communication. The clustering effect allows these companies to enjoy innovation and synergies from local knowledge spillovers, shared resources, and supportive ecosystems.



\section{Question 2}

\subsection{}

\begin{enumerate}
    \item Doctorate graduates: It measures and reflects a high level of education and research competence. However, while this indicates a workforce equipped with advanced problem-solving skills, the economic benefits of this indicator may not be immediately apparent if there are not enough job opportunities to absorb these graduates.
    \item Venture capital expenditures: It measures venture capital investment as a percentage of GDP. High levels of venture capital spending indicate confidence in start-ups and innovative projects, helping to drive high-growth companies. However, this index is highly volatile and significantly affected by macroeconomic conditions, which does not necessarily guarantee the success of innovative projects.
    \item International scientific co-publications: It measures the number of scientific publications co-authored by researchers from different countries. It is an important indicator for assessing international cooperation and knowledge exchange. The number of international co-authored scientific publications per million people shows an increase in the quality and impact of research. However, this indicator focuses on academic results, rather than the commercialization or practical application of these research results, and therefore does not directly reflect the overall picture of innovation capacity.
    \item Employment in knowledge-intensive activities: It measures the share of total employment in highly knowledge-intensive industries. This indicator reflects the economy's focus on high-value, innovation-driven industries, indicating the potential for high productivity and technological advancement. However, a high share of employment in knowledge-intensive activities does not necessarily lead to broad economic benefits if other sectors are neglected.
    \item PCT patent applications: It measures the number of international patent applications filed under the Patent Cooperation Treaty (PCT). This indicator reflects the level of innovation and technological development in a country, as well as its ability to protect intellectual property rights globally. However, the number of patent applications does not guarantee the commercial success of these innovations or their contribution to economic growth.
\end{enumerate}


\subsection{}

While the Comprehensive Innovation Index (SII) provides a concise overview of national innovation performance, facilitating international comparisons and trend analysis by policymakers and stakeholders, it has also faced criticism. Edquist et al. (2018) point out that by aggregating multiple indicators into a single score, SII may mask important differences between individual indicators, leading to an oversimplification and potentially misleading view of innovation systems. The composite score may not reflect the complexity and diversity of innovative activities, thus affecting targeted policy formulation.

\subsection{}

Based on Marxt and Brunner's analysis, the Swiss innovation system has strong R\&D capabilities and a highly developed education system, especially in terms of PhD graduates and lifelong learning, which is also verified by the European Innovation Scoreboard. Switzerland has excelled in international scientific collaboration and highly cited publications, demonstrating strong research capabilities and global reach. In addition, Switzerland performs well in exports of high-tech goods and knowledge-intensive services, indicating that its innovations are competitive in the global market.

However, there are some weaknesses in the Swiss innovation system. Despite strong R\&D capabilities, government support for corporate R\&D is weak, which may limit the private sector's incentive to innovate. Innovation cooperation among smes also needs to be strengthened, indicating that there is room for improvement in networking and collaboration among enterprises. In addition, broadband penetration is relatively low, which could affect the development of digital transformation and connectivity. Addressing these shortcomings will help improve Switzerland's innovation system across the board.

\subsection{}

To improve the Swiss innovation level, the following strategies can be considered:

Increase government support for corporate research and development and encourage private sector innovation.

Strengthen the collaboration between industry and academia to enhance the commercialization of research results.

Attract international talent while investing in lifelong learning progr